Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-05-31 04_paper/Draft2.Rmd
commiting some minor edits

abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving? We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
---

@@

However, many observe an unmistakable connection between China’s version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls “South-South cooperation.” While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. @mattingly_when_2021 use experiments to demonstrate that investing in both foreign aids and public diplomacy efforts can improve its image abroad and reduce concerns about the threat it poses. Both foreign aids and public diplomacy are scarce resources for government to build bilateral relationships and improve its image abroad. It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and invest in bilateral relationships through aids, mediated public diplomacy and diplomatic visits. To our knowledge, none of the existing studies examine systematically which countries are “friends” to get more benefits of aids from the perspective of Beijing’s diplomacy efforts. We conceptualize two opposite modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open. So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionally larger China’s foreign aid. We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. Both dimensions are important to build its public diplomacy efforts. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. All else equal, we argue that developing countries that receive higher media coverage and diplomatic visit are strategically more important than the others.

@@

This work further helps in dispelling the notion that China purposely engages in development finance in secret. Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage. To our understanding, this is the first attempt to use media agenda-setting and public diplomacy decision to explain Chinese foreign aids allocations. At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to aid-needed developing countries, are all crucial to achieving a state’s foreign policy goals and promoting its soft power.

@@

To assess complementarities between China's bilateral diplomatic visits and **Xinhua** coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources. We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition **Xinhua** news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. The full dataset consists of unique recipient-year observations from 2000 to 2014.

@@

>>>>

abstract: "China's international development finance has been long suspecpted to serve Beijing's efforts to promote its legitamcy and image on the world stage and to support closer ties with aid recipients. But what is puzzling is that these goals require transparency and publicity of development projects, which are two virtues China's development finance has historically lacked. We bring a novel perspective to this issue by considering how China's foreign aid complements more visible foreign policy levers Beijing may use to accomplish its goals: (1) state run media coverage of developing countries intended for foreign audiences and (2) bilateral diplomatic visits. These activities capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance is intended to support these goals, we expect greater coverage of a developing country in Chinese media directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation maps to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
---

@@

However, many observe an unmistakable connection between China’s version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls “South-South cooperation.” While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. @mattingly_when_2021 use experiments to demonstrate that investing in both foreign aid and public diplomacy efforts can improve China's image abroad and reduce concerns about the threat it poses. Importantly, both foreign aid and public diplomacy are scarce resources for building bilateral relationships and improving one's image abroad. It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and to invest in bilateral relationships through aid, mediated public diplomacy, and diplomatic visits.

We conceptualize two distinct but complementary modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open. So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionately larger China’s foreign aid. We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. Both dimensions are important to build its public diplomacy efforts. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. All else equal, we argue that developing countries that receive higher media coverage and diplomatic visit are strategically more important than the others.

@@

This work further helps in dispelling the notion that China purposely engages in development finance in secret. Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage. To our understanding, this is the first attempt to use media agenda-setting and public diplomacy to explain Chinese foreign aids allocations. At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to developing countries are all crucial to Beijing achieving its foreign policy goals and promoting its soft power.

@@

To assess complementarities between China's bilateral diplomatic visits and state sponsored media coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources. We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. The full dataset consists of unique recipient-year observations from 2000 to 2014.

@@

```{r, echo=FALSE}
coef_table <- map_dfr(
  model_list,
  ~ estimatr::tidy(lmtest::coeftest(.x))
) %>%
  filter(
    str_detect(term, "count") | 
      str_detect(term, "visits")
  ) %>%
  mutate(
    conf.low = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error,
    term = rep(c("Coverage", "Visits"), len = n())
  ) %>%
  select(term, estimate, conf.low, conf.high)
tibble(
  "1" = coef_table$term[1:2],
  "2" = coef_table$estimate[1:2],
  "3" = " ",
  "4" = coef_table$estimate[3:4],
  "5" = " ",
  "6" = coef_table$estimate[5:6],
  "7" = " ",
  "8" = coef_table$estimate[7:8],
  "9" = " ",
  "10" = coef_table$estimate[9:10],
  "11" = " ",
  "12" = coef_table$estimate[11:12],
  "13" = " "
) %>% 
  mutate_if(is.numeric, function(x) round(x, 2)) %>%
  kable(booktabs = T,
        format = "latex",
        caption = "Table 1: Model Estimates",
        col.names = c(
          " ", rep(c("Est.", "95% CI"), len = 12)
        )) %>%
  kable_classic(full_width = F) %>%
  column_spec(
    3, image = spec_pointrange(
      x = coef_table$estimate[1:2],
      xmin = coef_table$conf.low[1:2],
      xmax = coef_table$conf.high[1:2],
      vline = 0
    )
  ) %>%
  column_spec(
    5, image = spec_pointrange(
      x = coef_table$estimate[3:4],
      xmin = coef_table$conf.low[3:4],
      xmax = coef_table$conf.high[3:4],
      vline = 0
    )
  ) %>%
  column_spec(
    7, image = spec_pointrange(
      x = coef_table$estimate[5:6],
      xmin = coef_table$conf.low[5:6],
      xmax = coef_table$conf.high[5:6],
      vline = 0,
      lim = c(0, max(coef_table$conf.high[5:6]))
    )
  ) %>%
  column_spec(
    9, image = spec_pointrange(
      x = coef_table$estimate[7:8],
      xmin = coef_table$conf.low[7:8],
      xmax = coef_table$conf.high[7:8],
      vline = 0
    )
  )%>%
  column_spec(
    11, image = spec_pointrange(
      x = coef_table$estimate[9:10],
      xmin = coef_table$conf.low[9:10],
      xmax = coef_table$conf.high[9:10],
      vline = 0
    )
  ) %>%
  column_spec(
    13, image = spec_pointrange(
      x = coef_table$estimate[11:12],
      xmin = coef_table$conf.low[11:12],
      xmax = coef_table$conf.high[11:12],
      vline = 0
    )
  ) %>%
  add_header_above(
    c(
      " " = 1,
      "Linear" = 2,
      "Tobit" = 2,
      "Selection" = 2,
      "Level" = 2,
      "IV Lag" = 2,
      "IV Lewbel" = 2
    )
  ) %>% cat

```

### 2022-05-31 04_paper/slides.Rmd
commiting some minor edits

\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathabx}
\usepackage{mathpazo}
\usepackage{eulervm}
\usepackage{natbib}

@@

\begin{itemize}
    \item China seems to deliberately keep its foreign aid giving a secret.
    \item However, development finace arguably should promote "South-South cooperation" and improve China's image abroad.
    \item \textit{Such goals require transparency, so what should we make of its absence?}
\end{itemize}

@@

\begin{itemize}
\item \textbf{The Puzzle}: \textit{Absent formal modes of transparency, what evidence do we have that Chinese aid serves public diplomacy?}
\item \textbf{Argument}: \textit{We should observe complementarties between where China sends a greater number of diplomatic missions and that receive greater media coverage in outlets targeted at foreign audiences with where China gives greater foreign aid.}
\end{itemize}

@@

\begin{itemize}
    \item State-sponsored \textit{Xinhua} mediac coverage of developing countries intended for foreign audiences
    \item China’s bilateral South-South diplomatic activities

@@

Developing countries that receive \textbf{higher} media coverage and diplomatic visit are strategically more important than the others. Hence, they get \textbf{more} aid.

@@

Like Western donors, China should have an interest in generating goodwill toward Beijing.

\begin{itemize}
    \item US cites benefits from public branding of tsunami relief to Indonesia in 2004.
    \item Surveys of policymakers show increasing influence of Beijing.
\end{itemize}

The obscurity seems to have more to do with capacity and logistics, rather than intention \begin{footnotesize} (Dreher et al. 2018) \end{footnotesize}. We
explore the \textbf{connections }between China’s bilateral development finance and other, visible,
activities linked to diplomatic and legitimacy-seeking objectives.

@@

\begin{itemize}
\item What's covered in the news signals to the public what is important \begin{footnotesize} (McCombs \& Shaw, 1972) \end{footnotesize}

@@

\item \textit{Xinhua} has dual roles: reporting news and building the China
image as part of Beijing’s “going out” strategy \begin{footnotesize} (Shambaugh, 2015) \end{footnotesize}

@@

\item Diplomatic visit is a signal of support and closeness of countries.

@@

\item We expect China to prioritize giving foreign
aid to its “friends” -- countries where China has developed strong relationships through
public diplomacy efforts -- and to countries it seeks to highlight to Western audiences.

@@

\begin{itemize} 
    \item \textit{H1:} When developing countries receive more media exposure in \textit{Xinhua}, they are more
likely to receive more foreign aid from China.
    \item \textit{H2:} When developing countries host Chinese high-level diplomatic visits more
frequently, they are more likely to receive more foreign aid from China.
\end{itemize}

@@

Unique recipient-year observations from 2001 to 2014

@@

\item IV: counts of country media coverage (Millions of English edition \textit{Xinhua} news articles scraped by the Cline Center for Advanced Social Research)

@@

\item Covariates: aid recipient characteristics (GDP, presence of civil war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances)

\item Model Specifications: $\text{ihs(aid}_{rt}) = \tau_t + \beta_1\text{ihs(coverage}_{rt}) + \beta_2\text{ihs(visits}_{rt}) + X_{rt}^\top \gamma + \epsilon_{rt}.$

\item Estimation: OLS (CR1 errors), Tobit (random recipient intercepts), Logit/Selection (random recipient intercepts), Level/OLS (CR1 errors), Lagged IV (CR1 errors), Lewbel IV (CR1 errors).

@@

\begin{frame}{Conclusion}

\begin{itemize}
    \item Despite a lack of formal transparency China's foreign aid serves a public role.
    \item Beijing's development finance complements its efforts at south-south diplomacy.
    \item And its development finance complements media coverage of aid recipients targted at Western audiences.
\end{itemize}

\textbf{Like Western donors, visibility foreign aid serves China’s interests.}
\end{frame}

\end{document}

>>>>

---
output: beamer_presentation
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage[T1]{fontenc}
  - \usepackage{mathabx}
  - \usepackage{mathpazo}
  - \usepackage{eulervm}
  - \usepackage{natbib}
---

@@

\begin{itemize}
    \item China seems to deliberately keep its foreign aids secret
    \item However, aids as part of the "South-South cooperation" improve China's image abroad.
    \item Two opposite modes of interactions: foreign aids and media/public diplomacy -- secret and open
\end{itemize}

@@

\begin{itemize}
    \item Research Question: How does China’s foreign aid relate to Beijing’s efforts at public diplomacy and international recognition?

   \item Argument: Countries that receive higher media exposure and diplomacy efforts are
strategically more important to Beijing, and in turn receive disproportionally larger China’s
foreign aid.

\end{itemize}
\end{frame}

@@

\begin{itemize}
    \item state-sponsored \textit{Xinhua} mediac coverage of developing countries intended for foreign audiences
    \item China’s bilateral South-South diplomatic activities

@@

Developing countries that receive \textbf{higher} media coverage and diplomatic visit are strategically more important than the others. Hence, they get \textbf{more} benefits of aids.

@@

Similar to Western donors, the transparency of foreign aid arguably serve China’s interests.
\end{frame}

\begin{frame}{Motivations behind Chinese Foreign Aid}
The obscurity seems to have more to do with capacity and logistics, rather than intention \begin{footnotesize} (Dreher et al. 2018) \end{footnotesize}. We
explore the \textbf{connections }between China’s bilateral development finance and other, visible,
activities linked to diplomatic and legitimacy-seeking objectives.

@@

\begin{itemize}
\item What's covered in the news signal to the public what is important \begin{footnotesize} (McCombs \& Shaw, 1972) \end{footnotesize}

@@

\item Xinhua has dual roles: reporting news and building the China
image as part of Beijing’s “going out” strategy \begin{footnotesize} (Shambaugh, 2015) \end{footnotesize}

@@

\item Diplomatic visit is a signal of support and proximity of
the countries.

@@

\item We expect China to prioritize giving foreign
aid to its “friends” -- countries where China has developed strong relationships through
public diplomacy efforts.

@@

\begin{itemize} 
    \item \textit{H1:} When developing countries receive more media exposure in Xinhua, they are more
likely to receive more foreign aid from China.
    \item \textit{H2:} When developing countries host or visit Chinese high-level diplomatic visits more
frequently, they are more likely to receive more foreign aid from China.
\end{itemize}

@@

Unique recipient-year observations from 2000 to 2014

@@

\item IV: counts of country media coverage (Millions of English edition Xinhua news articles scraped by the Cline Center for Advanced Social Research)

@@

\item Covariates: aid recipient characteristics (GDP, presence of war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances)

\item Model Specifications: OLS with robust standard errors clustered by recipients; Tobit maximum likelihood estimator; selection and level equations; instrumental variables

@@

### 2022-05-31 04_paper/slides.tex
commiting some minor edits

---
output: beamer_presentation
header-includes:
  - \usepackage[utf8]{inputenc}
  - \usepackage[T1]{fontenc}
  - \usepackage{mathabx}
  - \usepackage{mathpazo}
  - \usepackage{eulervm}
  - \usepackage{natbib}
---

%% Load the markdown package
\usepackage[citations,footnotes,definitionLists,hashEnumerators,smartEllipses,tightLists=false,pipeTables,tableCaptions,hybrid]{markdown}
%%begin novalidate
\markdownSetup{rendererPrototypes={
 link = {\href{#2}{#1}},
 headingOne = {\section{#1}},
 headingTwo = {\subsection{#1}},
 headingThree = {\begin{frame}\frametitle{#1}},
 headingFour = {\begin{block}{#1}},
 horizontalRule = {\end{block}}
}}

%%end novalidate

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Results}

@@

\caption{Model Estimates}
\centering
\begin{tabular}[t]{lr>{}lr>{}lr>{}lr>{}lr>{}lr>{}l}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Linear} & \multicolumn{2}{c}{Tobit} & \multicolumn{2}{c}{Selection} & \multicolumn{2}{c}{Level} & \multicolumn{2}{c}{IV Lag} & \multicolumn{2}{c}{IV Lewbel} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13}
  & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI\\
\midrule
Coverage & 0.63 & \includegraphics[width=0.67in, height=0.17in]{} & 1.29 & \includegraphics[width=0.67in, height=0.17in]{} & 0.18 & \includegraphics[width=0.67in, height=0.17in]{} & 0.11 & \includegraphics[width=0.67in, height=0.17in]{} & 0.67 & \includegraphics[width=0.67in, height=0.17in]{} & 0.51 & \includegraphics[width=0.67in, height=0.17in]{}\\
Visits & 0.93 & \includegraphics[width=0.67in, height=0.17in]{} & 1.54 & \includegraphics[width=0.67in, height=0.17in]{} & 0.21 & \includegraphics[width=0.67in, height=0.17in]{} & 0.36 & \includegraphics[width=0.67in, height=0.17in]{} & 1.08 & \includegraphics[width=0.67in, height=0.17in]{} & 1.38 & \includegraphics[width=0.67in, height=0.17in]{}\\
\bottomrule
\end{tabular}
\end{table}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathabx}
\usepackage{mathpazo}
\usepackage{eulervm}
\usepackage{natbib}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\author{}
\date{\vspace{-2.5em}}

\begin{frame}
\%\% Load the markdown package

\usepackage[citations,footnotes,definitionLists,hashEnumerators,smartEllipses,tightLists=false,pipeTables,tableCaptions,hybrid]{markdown}

\%\%begin novalidate \markdownSetup{rendererPrototypes={
 link = {\href{#2}{#1}},
 headingOne = {\section{#1}},
 headingTwo = {\subsection{#1}},
 headingThree = {\begin{frame}\frametitle{#1}},
 headingFour = {\begin{block}{#1}},
 horizontalRule = {\end{block}}
}}

\%\%end novalidate

@@

\textbackslash begin\{document\}

@@

\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%

@@

\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%\%

\textbackslash begin\{frame\}\{Results\}

@@

\caption{Model Estimates}
\centering
\begin{tabular}[t]{lr>{}lr>{}lr>{}lr>{}lr>{}lr>{}l}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Linear} & \multicolumn{2}{c}{Tobit} & \multicolumn{2}{c}{Selection} & \multicolumn{2}{c}{Level} & \multicolumn{2}{c}{IV Lag} & \multicolumn{2}{c}{IV Lewbel} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13}
  & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI & Est. & 95\% CI\\
\midrule
Coverage & 0.63 & \includegraphics[width=0.67in, height=0.17in]{} & 1.29 & \includegraphics[width=0.67in, height=0.17in]{} & 0.18 & \includegraphics[width=0.67in, height=0.17in]{} & 0.11 & \includegraphics[width=0.67in, height=0.17in]{} & 0.67 & \includegraphics[width=0.67in, height=0.17in]{} & 0.51 & \includegraphics[width=0.67in, height=0.17in]{}\\
Visits & 0.93 & \includegraphics[width=0.67in, height=0.17in]{} & 1.54 & \includegraphics[width=0.67in, height=0.17in]{} & 0.21 & \includegraphics[width=0.67in, height=0.17in]{} & 0.36 & \includegraphics[width=0.67in, height=0.17in]{} & 1.08 & \includegraphics[width=0.67in, height=0.17in]{} & 1.38 & \includegraphics[width=0.67in, height=0.17in]{}\\
\bottomrule
\end{tabular}
\end{table}
\end{frame}

\end{document}
